\subsection{Proof of select lemmas}

%\begin{problem}{\algprobm{Comp-3DM}}
%    \tab \textbf{Input:}
%    \tab \textbf{Decide:}
%\end{problem}

\begin{claimproof}{Lemma \ref{lem:red1} or
                    \algprobm{3DM} $\mred$ \algprobm{DodgsonScore}}\\
    Our reduction differs from \citet{bartholdiVoting}
    in that our reduction has additional properties that are required
    by the lemma.
    We will reduce from \algprobm{ThreeDimensionalMatching} to \dscore:

\begin{problem}{\algprobm{ThreeDimensionalMatching} (\algprobm{3DM})}\\
    \tab \textbf{Input:} Sets $M,W,X,Y$, where $M\subseteq W \times
    X \times Y$ and $W,X,Y$ are disjoint, nonempty sets having the
    same number of elements.\\
    \tab \textbf{Decide:} Does $M$ contain a matching, i.e. a subset
    $M' \subseteq M$ such that $\mathnormal{M'} = \mathnormal{W}$
    and no two elements of $M'$ agree in any coordinate?
\end{problem}


\end{claimproof}

\begin{claimproof}{Lemma \ref{lem:2er}}\\
    We will reduce from \csat to \algprobm{2ER}.
    Let $\langle A,B \rangle$ be a \csat instance.

    For each 3CNF formula $x \in A$ or $B$, reduce $x$ into
    the corresponding \algprobm{3DM} instance $x'$ and add $x'$
    to $A'$ or $B'$ if $x\in A$ or $x \in B$, respectively.
    In effect we are reducing \csat to an instance of
    \algprobm{Comp-3DM}, $\langle A', B' \rangle$.
    It is easy to see that solving $\langle A', B' \rangle$
    solves $\langle A, B \rangle$.

    Now we perform a similar reduction from \algprobm{Comp-3DM}
    to \algprobm{Comp-DodgsonScore}.
    For each $x' \in A'$ or $B'$, use the function in
    Lemma \ref{lem:red1} to reduce $x'$ into the corresponding
    \dscore instance $\dtriple$ and add $\dtriple$
    to $A''$ or $B''$ if $x'\in A'$ or $x' \in B'$, respectively.
    It is similarly easy to see that solving $\langle A'', B'' \rangle$
    solves $\langle A', B' \rangle$.
    If $x' \in$ \algprobm{Comp-3DM} then by Lemma \ref{lem:red1}
    $Score(\dtriple) = k$ and thus \dscore on $\dtriple$ returns yes.
    If $x' \notin$ \algprobm{Comp-3DM} then
    $Score(\dtriple) = k+1$ and \dscore on $\dtriple$ returns no.

    Now we reduce from \algprobm{Comp-DodgsonScore} to \algprobm{2ER}
    using Lemma \ref{lem:merge1}.
    First note that the direction of the inequality of the decision problem
    changes in this reduction by the nature of Lemma \ref{lem:red1}.
    Now to begin the reduction, we merge all the Dodgson elections
    in $A'', B''$ into $\langle C,c,V \rangle$ and $\langle D,d,W \rangle$,
    respectively.
    This is done using the $DodgsonSum$ function in \ref{lem:merge1}.
    For example if $A'' = \dtripnum{1},\dtripnum{2}, \dots, \dtripnum{k}$
    then

    \[\dtriple = DodgsonSum(\langle \dtripnum{1},\dtripnum{2}, \dots,
    \dtripnum{k}) \rangle)\]

    and

    \[\sum_j Score(\dtripnum{j}) =
    Score(\dtriple).\]

    Now $\langle A'', B'' \rangle$ being true is equivalent to
    the number of satisfied \dscore instances in $A''$ being greater than
    that of $B''$.
    This again is equivalent to the sum of the Dodgson
    scores of $A''$ being less than that of $B''$.
    Thus using the reduction of $\langle A'', B'' \rangle$ outlined above,
    If $Score(\langle C,c,V \rangle)\leq Score(\langle D,d,W \rangle)$ is true,
    then $\langle A'', B'' \rangle$ is true and similarly for the false case.
    Hence we have shown a reduction from \algprobm{Comp-DodgsonScore} to
    \algprobm{2ER}.

    Combining the many-one reductions above, we have shown that:

    \[\text{\csat} \mred \text{\algprobm{Comp-3DM}} \mred
    \text{\algprobm{Comp-DodgsonScore}} \mred
    \text{\algprobm{2ER}}.\]

    So by Theorem \ref{thm:csat}, \algprobm{2ER} is \tp-hard and the
    Lemma is proved.
\end{claimproof}

\subsection{Proof that \algprobm{DodgsonWinner} is \tp-complete.}
\begin{claimproof}{Theorem \ref{thm:dwin}}\\
    By Theorem \ref{thm:intp}, \dwin $\in$ \tp.
    We now show that \algprobm{2ER} $\mred$ \dwin.


\end{claimproof}