\section{The Complexity of the Dodgson Winner Problem}
Our results largely follow the proof in \citet{exactdodgson}, except instead of
using a technical lemma by \citet{wag90}, we instead begin the reduction
with the recent result that \algprobm{Comp-SAT} is \tp-complete \citep{compsat}.
All lemmas and theorems in this section
unless cited otherwise are from \citet{exactdodgson}.
We have omitted proofs of technical lemmas and have used our own proof of Lemma
\ref{lem:2er}, which is the main hardness proof.

We first state the main result of this section and a big-picture corollary
concerning the polynomial hierarchy.

\begin{theorem}\label{thm:dwin}
    \algprobm{DodgsonWinner} is \tp-complete
\end{theorem}

It follows that though \algprobm{DodgsonWinner} is \np-hard \citep{bartholdiVoting},
it cannot be \np-complete unless the polynomial hierarchy collapses.

\begin{corollary}
    If \algprobm{DodgsonWinner} is \np-complete then \cc{PH} = \np.
\end{corollary}

\subsection{Outline of Proof of Theorem \ref{thm:dwin}} \label{subsec:outline}
    First we briefly outline the reduction from Comp-SAT to
DodgsonWinner.
    All of the following reductions are many-one reductions.
Let us start with a \csat instance $\langle A,B \rangle$.
For each 3CNF
formula $x$ in $A$ and $B$, reduce $x$ into the corresponding instance of
\algprobm{ThreeDimensionalMatching} (\algprobm{3DM}), which is possible because
\algprobm{3DM} is \np-complete.
Now, for each \algprobm{3DM} problem, we reduce it into an instance of
\dscore.
Using a merger lemma, we will merge these two sets of
\dscore~instances into two elections, one for $A$
and one for $B$, thus an yielding
instance of \algprobm{2ElectionRanking} (\algprobm{2ER}).
Then \algprobm{2ER} will be reduced to DodgsonWinner.
For the formal proof we will use the problems \algprobm{Comp-3DM} and
\algprobm{Comp-DodgsonScore} which are similar to \csat.
Alternatively, one could replace some of these reductions with
polynomial time truth-table reductions.

A reference diagram is provided:

\[\text{\csat} \mred \text{\algprobm{Comp-3DM}} \mred
\text{\algprobm{Comp-DodgsonScore}} \mred
\text{\algprobm{2ER}} \mred \text{\algprobm{DodgsonWinner}}\]

This reduction can be further truncated by using Theorem 1 after showing
that \dscore~ is \np-complete.
We would be immediately be able to establish that \algprobm{Comp-DodgsonScore}
is \tp-hard.
However we leave in the other steps to reduce from a candidate for a canonical
problem for the class \tp.
Once the reduction above is proved, it remains to show membership in \tp~in order
to prove Theorem \ref{thm:dwin}.
\begin{theorem} \label{thm:intp}
    \algprobm{DodgsonWinner} $\in$ \tp. \\
\end{theorem}
\begin{proof}
    Ask in parallel all the \algprobm{DodgsonScore} queries,
    one for each candidate in $C$.
    Each query is an \np~query since \algprobm{DodgsonScore} is \np-complete by
    the second reduction outlined above (lemma \ref{lem:red1}) and observing
    that given a yes-answer, it can be justified in polynomial time by
    identifying appropriate switches and tabulating the vote.
    We now have the exact Dodgson Score for each candidate (do binary search
    over the potential scores, which is polynomial in the input size).
    It is easy to decide
    whether or not the given candidate $c$ has the minimum score
    (find the max of the scores and compare the $c$'s score to
    the max $\sim\mathcal{O}(n)$).
\end{proof}

The rest of the section will be devoted to proving the reduction outlined above.

\subsection{Outline of relevant lemmas}

In order to prove the reduction outlined in section \ref{subsec:outline},
we first state the necessary lemmas.
Proofs of the non-technical lemmas will be provided in section \ref{subsec:pflem}.
What these lemmas provide are ways to add election scores, and how to merge elections.
The main part of the reduction is reducing from \csat to \algprobm{2ER}
from which a merger lemma is needed to reduce to \dwin.

The first part of the reduction is performed by the following lemma.

\begin{lemma} \label{lem:red1}
    There exists an \np-complete problem $A$ and a polynomial-time
    computable function $f$ that reduces $A$ to \dscore~in such
    a way that, $\forall x \in \Sigma^*,
    f(x) = \langle \langle C,c,V \rangle, k\rangle $
    is an instance of \dscore~with an odd number of voters and
    \begin{enumerate}
        \item if $x\in A$ then $Score(\dtriple) = k$, and
        \item if $x\notin A$ then $Score(\dtriple) = k+1$.
    \end{enumerate}
\end{lemma}

\begin{lemma} \label{lem:merge1}
    There exists a polynomial-time computable function
    $DodgsonSum$ such that $\forall k$ and for all\\
    $\dtripnum{1},\dtripnum{2}, \dots, \dtripnum{k}$ satisfying
    $||V_j||$ is odd for all $ j$, it holds that
    \[DodgsonSum(\langle \dtripnum{1},\dtripnum{2}, \dots,
    \dtripnum{k}) \rangle)\]
    is a Dodgson triple having an odd number of voters and such that
    \[\sum_j Score(\dtripnum{j}) =
    Score(DodgsonSum(\langle \dtripnum{1},\dtripnum{2}, \dots,
    \dtripnum{k}) \rangle)\]
\end{lemma}

Theorem \ref{thm:csat}, Lemma \ref{lem:red1} and Lemma
\ref{lem:merge1}, establish the \tp-hardness of a problem related to
\algprobm{DodgsonWinner}. We now define this decision problem:

\begin{problem}{\algprobm{TwoElectionRanking} (\algprobm{2ER})} \\
    \tab Instance: A pair of Dodgson triples
$\langle \langle C,c,V \rangle, \langle D,d,W \rangle \rangle$
both having an odd number of voters such that $c\neq d$.\\
    \tab Decide: Is 
$Score(\langle C,c,V \rangle)\leq Score(\langle D,d,W \rangle)$?
\end{problem}

\begin{lemma} \label{lem:2er}
    \algprobm{2ER} is \tp-hard.
\end{lemma}

We now need to make the results so far applicable to 
\algprobm{DodgsonWinner}, so we need another merger lemma to
merge two elections into a single election.

\begin{lemma} \label{lem:merge2}
There exists a polynomial-time computable function $Merge$
    such that, for all Dodgson triples,
    $\langle C,c,V \rangle$ and $\langle D,d,W \rangle$ 
    for which $c\neq d$ and both having an odd number of voters,
    there exist $\hat{C}$ and $\hat{V}$ such that
    \begin{enumerate}
        \item $Merge(\langle C,c,V \rangle, \langle D,d,W \rangle)$
        is an instance of \algprobm{DogsonWinner}, 
        \item $Merge(\langle C,c,V \rangle, \langle D,d,W \rangle)
        = \langle \hat{C},c,\hat{V} \rangle$,
        \item $Score(\langle \hat{C},c,\hat{V} \rangle) =
        Score(\langle C,c,V \rangle) + 1$,
        \item $Score(\langle \hat{C},d,\hat{V} \rangle) =
        Score(\langle D,d,W \rangle) + 1$ and,
        \item for each $e \in \hat{C}\setminus \{c,d\}$, 
        $Score(\langle \hat{C},c,\hat{V} \rangle) < 
        Score(\langle \hat{C},e,\hat{V} \rangle)$
    \end{enumerate}
\end{lemma}



